### 2021-03-01 results.tex
additional review related to the malware examples

The Venn-diagram of Figure~\ref{fig:venn-plot1}
summarizes how the tools can complement each other.
Note in the diagram that $53$ malwares have been detected by all sandboxes generated in the first execution (with the DroidFax static analysis algorithms), out of the 78 identified by at least one sandbox. In addition, the DroidBot sandbox did not detect any malware that had not been detected by the other tools. Differently, the Monkey's sandbox detected three malwares that had not been detected by any other sandbox, DroidBot sandbox detected two malwares that had not been detected by any other sandbox, and Humanoid detected one malware that had not been detected by any other sandbox. Contrasting with the \blls,
our results suggest that using DroidBot in combination with Monkey, DroidMate, and Humanoid does not improve the general performance of an integrated environment for mining
Android sandboxes.

@@

Altogether, ignoring the \joke tool, our study reveals that from $58.33$\% (Humanoid)
to $76.04$\% (DroidBot) of the malicious apps investigated in our study can be
detected using the sandboxes generated after running the test case tools with the support of DroidFax static analysis algorithms. Besides that, in the first execution, none of the resulting sandboxes could detect 18 malwares in our dataset ($18.75$\%). According to the Euphony tool~\cite{hurier2017euphony}, $12$ of these $18$ malwares are \emph{adwares}, $3$ are \emph{trojans}, $2$ are PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}. In what follows we present some characteristics of two malware that had not been detected by the sandboxes (mobi.infolife.cachepro) and (com.andoop.flyracing), both downloaded from alternative android market, anzhi~\cite{anzhi}.

The first listing refers to package (mobi.infolife.cachepro), which has a less dangerous malicious strategies, and just translate the app from English language to Chinese language. That modification, does not threaten the user's device, however it is a unwanted private app change, and can characterize as misappropriation app.

\begin{lstlisting}[caption= smali/mobi/infolife/cachepro/h.smali - (mobi.infolife.cachepro),language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:mobi.infolife.cachepro}]

1:B < const-string v3, "Swith To "
---
1:M > const-string v3, "\u65e0\u6cd5\u542f\u52a8\u5e94\u7528\u201c"
\end{lstlisting}

\begin{lstlisting}[caption=AndroidManifest.xml - (com.andoop.flyracing), language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:app65}]

1:B < <meta-data android:name="ADMOB_PUBLISHER_ID"
                     android:value="a14cf7346295891"/>
---
1:M > <meta-data android:name="ADMOB_PUBLISHER_ID"
                     android:value="a14f099bfbf3c61"/>
\end{lstlisting}

The second listing refers to package (com.andoop.flyracing). Your malicious version change the Android Manifest file, modifying the identification of meta-data ADMOB\_PUBLISHER\_ID. AdMob \cite{admob} is a mobile app monetization service, provided by Google. The Publisher ID \cite{publisherID} is the unique identifier for the AdMob account, and may be used to authenticate communication with Google. With that change, the malware is changing the ad revenue destination.

Now we present an malicious app that was detected by 2 sandboxes. The package (com.gau.screenguru.finger) belongs to ours dataset, and is a troubling example. First it modify the Android Manifest file, adding permissions to receive and send SMS (Listing 3). Then, the malicious app use those permissions to performs MainService.java file, that get user's sensitive information, like International Mobile Equipment Identity (IMEI), and sink by SMS message (Listing 4). This malicious behaviours was detected by sandboxes builded by Droidbot and Humanoid tools.

\begin{lstlisting}[caption= AndroidManifest.xml - (com.gau.screenguru.finger), language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:com.gau.screenguru.finger:androidmanifest}]

@@

\begin{lstlisting}[caption= com/android/main/MainService.java - (com.gau.screenguru.finger), language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:(com.gau.screenguru.finger):mainservice}]

@@

%\rb{This is an interesting place to present the details of two or three malwares in this set of 19 malwares that had not been detected by any tool. I think Thales could work on this, since he has helped Handrick to dissect the malwares.}

>>>>

The Venn-diagram of Figure~\ref{fig:venn-plot1}
summarizes how the tools can complement each other.
Note in the diagram that $53$ malwares have been detected
by all sandboxes generated in the first execution (with the DroidFax static analysis algorithms),
out of the 78 identified by at least one sandbox. In addition, the DroidBot sandbox did not detect
any malware that had not been detected by the other tools. Differently, the Monkey sandbox detected
three malwares that had not been detected by any other sandbox, the DroidBot sandbox detected two malwares
that had not been detected by any other sandbox, and the Humanoid sandbox detected one malware that had not
been detected by any other sandbox. Contrasting with the \blls,
our results suggest that using DroidBot in combination with Monkey, DroidMate, and Humanoid
does not improve the general performance of an integrated environment for mining
Android sandboxes.

@@

Altogether, ignoring the \joke tool, our study reveals that from $58.33$\% (Humanoid)
to $76.04$\% (DroidBot) of the malicious apps investigated in our study can be
detected using the sandboxes generated after running the test case tools with the support of the
DroidFax static analysis algorithms. Besides that, in the first execution, none of the
resulting sandboxes could detect 18 malwares in our dataset ($18.75$\%). According to
the Euphony tool~\cite{hurier2017euphony}, $12$ of these $18$ malwares are \emph{adwares}, $3$ are \emph{trojans}, $2$ are
PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}.

The DroidBot and Humanoid sandboxes detected the malicious version of the app
\texttt{com.andoop.flyracing}. In this particular case,
the malicious version changed the Android Manifest file,
adding permissions to receive and send SMS messages
(Listing~\ref{lst:androidManifest}). Moreover, after decompiling
this malware, we also observed that the malicious version of the
\texttt{MainService} class introduced a
behavior that collects sensitive information (the International Mobile
Equipment Identity, IMEI) and sends it using an SMS message
(Listing~\ref{lst:mainService}).

\begin{lstlisting}[caption={Diffs in the \texttt{com.gau.screenguru.finger}
      AndroidManifest file of the malicious
      version}, language=Java,
    basicstyle=\fontsize{8}{6}\selectfont\ttfamily,
    label={lst:androidManifest}]

@@

\begin{lstlisting}[caption={Diffs in the malicious version
      of the class \texttt{com.android.main.MainService}
      (app \texttt{com.gau.screenguru.finger})},
      language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,
      label={lst:mainService}]

@@

%% In what follows we present some characteristics of two malwares
%% that had not been detected by the sandboxes (app \texttt{mobi.infolife.cachepro} and app \texttt{com.andoop.flyracing}).

%% In the first example (\texttt{mobi.infolife.cachepro}), the malicious behavior comprises changes to
%% the app idiom (Listing~\ref{lst:app65a}) and to the publisher identifier (Listing~\ref{lst:app65b}).
%% Although such a modification does not threaten the user's device,
%% it might characterize a scenario of app misappropiation.
%% Although such a modification does not threaten the user's device,
%% it might characterize a scenario of app misappropriation. That is, after manually dissecting this particular malware,
%% we did not identify any change with regard to calls to sensitive APIs or app behavior.

%% \begin{lstlisting}[caption= {Diff in the file \texttt{smali/mobi/infolife/cachepro/h.smali}. \texttt{B} stands for
%%     the benign version, while \texttt{M} stands for the malign version.},language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:app65a}]

%% 1:B < const-string v3, "Swith To "
%% ---
%% 1:M > const-string v3, "\u65e0\u6cd5\u542f\u52a8\u5e94\u7528\u201c"
%% \end{lstlisting}

Differently, none of the computed sandboxes detected the malicious version
of the app \texttt{com.andoop.flyracing}. Indeed,
the malicious version {\color{red}only} changes the
Android Manifest file, modifying the meta-data \texttt{ADMOB\_PUBLISHER\_ID}.
However, the AdMob is a monetization service provided by Google, and changing the
AdMob \emph{publisher identifier} account redirects the advertisement's
revenue to another destination.

\begin{lstlisting}[caption={Diff in the file \texttt{com.andoop.flyracing}
      AndroidManifest file of the malicious version.
      \texttt{B} stands for
      the benign version, while \texttt{M} stands for the malign version.}, language=XML,
    basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:app65b}]

1:B < <meta-data android:name="ADMOB_\PUBLISHER_\ID"
                     android:value="a14cf7346295891"/>
---
1:M > <meta-data android:name="ADMOB_\PUBLISHER_\ID"
                     android:value="a14f099bfbf3c61"/>
\end{lstlisting}
